Manuscript

### 2014-10-14 inst/simulation/manuscript.Rmd
...

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

p1 <- plotCIProportions(cip1)
saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
p2 <- plotCIProportions(cip2)
saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
p3 <- plotCIProportions(cip3)
saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)

```

>>>>

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

p1 <- plotCIProportions(cip1)
saveFigure(p1, "manuscript-figure-5a.png", width=4, height=2)
p2 <- plotCIProportions(cip2)
saveFigure(p2, "manuscript-figure-5b.png", width=4, height=2)
p3 <- plotCIProportions(cip3)
saveFigure(p3, "manuscript-figure-5c.png", width=4, height=2)
```
